An Open Platform for Managing Short Programming Exercises

### 2013-06-20 paper/paper.tex
philosophical questions
added a discussion question
more discussion questions from Jaime

>>>>

{\bf Given an effective mechanism for sharing curriculum materials, could
courses at a number of institutions converge towards an optimum?}
Discuss.

{\bf If exercises are shared freely, is the availability of solutions a concern?}
Discuss.

{\bf Should exercises be graded?}
Discuss.

{\bf What are the appropriate incentives to encourage students to attempt
the exercises (and get the maximum benefit from them)?}
Discuss.
